TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2019-07-30 paper/draft.tex
add new figures

@@

Compared to the \citealt{Casagrande:2008}, \citealt{Boyajian:2012}, and \citealt{Mann:2015} derived temperatures, we find ASPCAP overestimates $\teff$ on average by a bias of $130-170$K, while \thecannon\ underestimates $\teff$ by a bias of $\sim25$K. We also see the scatter is much higher for the ASPCAP temperatures ($\sim230$K) compared to the scatter of \cannon\ temperatures ($\sim85$K).

@@

>>>>

\begin{figure*}
\begin{center}
	\includegraphics[height=5cm]{figures/toomre.png}
	\includegraphics[height=5cm]{figures/met_hist.png}
	\caption{Toomre diagram showing the distribution of the \cannon\ metallicities (left). Dashed lines at $v_{tot}=70$\,km/s and 180\,km/s show roughly the separation of thin/thick/halo stars. Histogram (right) shows the metallicity distribution of thin and thick disk stars, with blue corresponding to $v_{tot}<70$\,km/s and green corresponding to $70<v_{tot}<180$\,km/s respectively. The average metallicities of the distribution of the thin disk stars are $\feh=0.00\pm0.17\,$dex, and the average metallicities of the thick disk stars are $\feh=-0.14\pm0.19\,$dex.}
	\label{fig:toomre}
\end{center}
\end{figure*}

\begin{figure}
\begin{center}
	\includegraphics[width=\linewidth]{figures/wide_binary_met.png}
	\caption{}
\end{center}
\end{figure}

@@

Compared to the \citealt{Mann:2015} and \citealt{Boyajian:2012} color-metallicity derived temperatures, both ASPCAP and \cannon\ temperatures show similar scatters of $\sim60\,$K, but offset by a constant.
We find \cannon\ to be in better agreement with \citealt{Mann:2015} and \citealt{Boyajian:2012}, with ASPCAP overestimating $\teff$ on average $\sim110-140\,$K, and \thecannon\ underestimating $\teff$ on average by $\sim10-20\,$K.

@@

As a check of internal consistency, we cross-matched our M dwarf final sample with the \citealt{Elbadry:2018b} catalog of $>$50,000 high-confidence, widely separated binaries identified by \drtwo.
